Concurrent Programming with CXL

### 2020-07-04 book/paper.tex
Latest

\newcommand{\cxllink}[1]{%
[\href{https://www.cs.cornell.edu/home/rvr/cxl/code/#1}{\underline{#1}}]%
}

@@

\begin{figure}
\begin{code}
\cxlsource{cs}
\end{code}
\caption{\cxllink{code/cx.cxl} CXL model of a critical section.}
\label{fig:cs}
\end{figure}

>>>>

\newcommand{\cxllink}[1]{%
[\href{https://www.cs.cornell.edu/home/rvr/cxl/#1}{\underline{#1}}]%
}

@@

\begin{figure}
\begin{code}
\cxlsource{cs}
\end{code}
\caption{\cxllink{code/csbarebones.cxl} CXL model of a critical section.}
\label{fig:cs}
\end{figure}
